\begin{center} \bf \sffamily \LARGE Prisoner's dilemma with stochastic payoffs\\[-1cm] \end{center}

### 2021-11-24 main.tex
testing something regarding line length
making a commit
working on the introduction

\begin{abstract}
% Repeated games are vastly used in evolutionary game theory to explain
% cooperation in a variety of environments. Although existing models have shaped
% our understanding of human cooperation, they often work with idealized
% assumptions. In an evolutionary process, individuals imitate other individuals
% of the population based on their fitness. It is commonly assumed that an
% individual computes their fitness after interacting with a representative sample
% of the population, and remembering all the interactions they participated in. In
% real life, we do not always remember all our interactions, instead we rather
% recall our most recent ones.

@@

Evolutionary game theory~\cite{smith1982evolution, hofbauer1998evolutionary,
nowak2004evolutionary, hauert2005game} describes the evolutionary dynamics of
populations consisting of different types of interacting individuals.
Traditional approaches assume that individuals meet each other at random in an
infinitely large well-mixed population. An example of such a approach in the the
replicator dynamics. It describes how the abundance of strategic types in a
population changes based on their fitness, identified with the payoff resulting
from the game~\cite{cressman2014replicator}. In this deterministic formulation,
individuals with higher fitness, such as defectors, increase in abundance.
Ultimately, the system reaches a stable fixed point in which the population may
consist either of a single type or of a mixture of different types.

It has been shown that the finiteness of populations may lead to fundamental
changes in this picture due to stochastic effects In this framework
disadvantageous mutants have a small, yet non-zero probability to reach fixation
in a finite population.

Its most prominent application is the quest for the origins and 
evolution of cooperation.
An important application of evolutionary game theory is the evolution of
cooperation which remains one of the greatest problems for biological and social
sciences.

% To explain the evolution of cooperation remains one of the greatest problems for
% biological and social sciences. Cooperation is the action of choosing to help
% others at one's own expense. The standard game of formulating such situation is
% the Prisoner's Dilemma~\cite{trivers1971evolution,
% milinski1987tit, glynatsi2021bibliometric, ohtsuki2006simple}, in which two
% players can choose to cooperate or to defect. The players are offered a certain
% payoff, \(R\), for mutual cooperation and a lower payoff, \(P\), for mutual
% defection. If one player cooperates while the other defects, then the cooperator
% gets the lowest payoff, \(S\), while the defector gains the highest payoff,
% \(T\). Thus, the payoffs have the following property \(T > R > P > S\), making
% defection the dominant strategy in the non-repeated game.

% In the repeated Prisoner's Dilemma, direct reciprocity can allow cooperators to
% not be exploited by defectors~\cite{axelrod1981evolution, nowak1992tit,
% nowak1992evolutionary}, however, how do such cooperators can evolve?

 , and 
in general, defectors are stable against invasion by cooperators.

In this framework disadvantageous mutants have a small, yet non-zero probability
to reach fixation in a finite population.

Two classes of microscopic processes have been used extensively: (i)
fitness-based processes in which an individual chosen proportional to fitness
reproduces and the offspring replaces a randomly chosen individual [11]; (ii)
pairwise comparison processes in which a pair of individuals is chosen, and
where subsequently one of these individuals may adopt the strategy of the other.

In the pairwise process considers a finite population of fixed size.In the
population at a time step different types of individuals can exist. 
Each individual can be of one of two types, A and B. The state of the population
is thus characterized by the number i of individuals of type A.

The interaction between the two types of individuals is described by the
functions $\pi _{{\rm A}}^{i}$ and $\pi _{{\rm B}}^{i}$. These indicate the
expected payoff for two types in a population in state i. The interaction can be
generated from a two-player matrix game which leads to payoffs linear in i [26],
but we keep the formalism general to include games played between an arbitrary
number of players, which leads to payoffs that depend on i in a polynomial way
[27–30]. In fact, our results hold for an arbitrary dependence of the payoffs on
i.

At each step an individual change their type based. This very cooperators
can repeas.

>>>>

\begin{abstract}
% Repeated games are vastly use in evolutionary game theory to explain cooperation in a variety of environments. Although existing models have shaped
% our understanding of human cooperation, hey often work with idealized
% assumptions. In an evolutionary process, individuals imitate other individuals
% of the population based on their fitness. It is commonly assumed that an
% individual computes their fitness after interacting with a representative sample
% of the population, and remembering all the interactions they participated in. In
% real life, we do not always remember all our interactions, instead we rather
% recall our most recent ones.

@@

Evolutionary game theory~\cite{smith1982evolution, hofbauer1998evolutionary,
nowak2004evolutionary, hauert2005game} describes the evolutionary dynamics of
populations consisting of different types of interacting individuals. The
framework of evolutionary game theory has been applied in %ToDo cite.
Traditional approaches of evolutionary game theory assume that individuals meet
each other at random in an infinitely large well-mixed population, such an
approach is the replicator dynamics. The replicator dynamics describes how the
abundance of strategic types in a population changes based on their fitness. In
this deterministic formulation, individuals with higher fitness increase in
abundance and ultimately, the system reaches a stable fixed point in which the
population may consist either of a single type or of a mixture of different
types. The works of cite have shown that by constrain the population to a
finiteness of populations may lead to fundamental changes in this picture due to
stochastic effects. These stochastic effects disadvantageous mutants have a
small, yet non-zero probability to reach fixation in a finite population.

Two classes of such finite stochastic processes have been used extensively: (i)
fitness-based processes in which an individual chosen proportional to fitness
reproduces and the offspring replaces a randomly chosen individual [11]
\textit{moran process}; (ii) \textit{pairwise comparison processes} in which a
pair of individuals is chosen, and where subsequently one of these individuals
may adopt the strategy of the other.

In pairwise comparison process considers a finite population of fixed size. In
the population at a time step different types of individuals can exist. In the
simplest of cases each individual can be of one of two types, A and B. The state
of the population is thus characterized by the number \(k\) of individuals of
type A. The interaction between the two types of individuals is described by the
functions \(\pi _{{\rm A}}^{i}\) and $\pi _{{\rm B}}^{i}$.

At each step an individual change their type based.

\begin{equation} \label{Eq:rho}
  \rho(\pi _{{\rm A}}^{i}, \pi _{{\rm B}}^{i}) = \frac{1}{1\!+\! \exp^{\!-\!\beta (\pi _{{\rm A}}^{i}\!-\!\pi _{{\rm B}}^{i})}}.
\end{equation}

The parameter denotes the intensity of selection. For , fitness equals payoff.
This scenario describes ``strong selection''. For \(\beta \ll 1\) , the
payoff only provides a small perturbation to the overall fitness of an
individual, a limit known as weak selection (Nowak et al., 2004).

These indicate the expected payoff for two types in a population in state i. The
interaction can be generated from a two-player matrix game which leads to
payoffs linear in i [26], but we keep the formalism general to include games
played between an arbitrary number of players, which leads to payoffs that
depend on i in a polynomial way [27–30]. In fact, our results hold for an
arbitrary dependence of the payoffs on i.

In the simplest case, the payoffs of A and B individuals only depend on the
fraction of both types in the population. If there are i A individuals and B
individuals, then the A and B individuals have payoffs and , respectively.
Self-interactions are excluded.

Here, we consider a process based on pairwise comparison between individuals.
Two individuals, A and B, are selected at random. The individual chosen for
reproduction A replaces B with probability p, which depends on the payoff
difference between the two individuals. The composition of the population can
only change if both individuals are of different types. We follow (Blume, 1993,
Szabó and Tőke, 1998, Hauert and Szabó, 2005) in choosing the Fermi function
from statistical physics for p

To explain the evolution of cooperation remains one of the greatest problems for
biological and social sciences. Cooperation is the action of choosing to help
others at one's own expense. The standard game of formulating such situation is
the Prisoner's Dilemma~\cite{trivers1971evolution,
milinski1987tit, glynatsi2021bibliometric, ohtsuki2006simple}, in which two
players can choose to cooperate or to defect. The players are offered a certain
payoff, \(R\), for mutual cooperation and a lower payoff, \(P\), for mutual
defection. If one player cooperates while the other defects, then the cooperator
gets the lowest payoff, \(S\), while the defector gains the highest payoff,
\(T\). Thus, the payoffs have the following property \(T > R > P > S\), making
defection the dominant strategy in the non-repeated game.

In the context of the prisoner's dilemma the payoffs are calculated as follows.
In the example that a strategy is playing always cooperate and always defect,
